---
title: "Align countries by number of cases"
---

```{r setup, include=FALSE}
library(tidyverse)
library(plotly)
knitr::opts_chunk$set(echo = FALSE)
```

```{r, child="childs/csse_tables_all.Rmd"}
```

```{r}
.plot_function <- function(data) {
    label_data <- data %>%
        group_by(`Country/Region`) %>% 
        top_n(1, Cases)
    fig <- plot_ly() 
    fig <- fig %>%
        add_trace(
            type = 'scatter',
            mode = 'lines+markers',
            x = data$`Days since 100th case`,
            y = data$Cases,
            color = data$`Country/Region`,
            text = data$`Country/Region`,
            hovertemplate = paste('<i>Cases</i>: %{y}',
                                '<br><b>Relative day</b>: %{x}<br>',
                                '<b>%{text}</b>'),
            showlegend = FALSE
      )
    fig <- fig %>% add_annotations(x = label_data$`Days since 100th case`,
                      y = label_data$Cases,
                      text = label_data$`Country/Region`,
                      xref = "x",
                      yref = "y",
                      showarrow = TRUE,
                      arrowhead = 4,
                      arrowsize = .5,
                      ax = 20,
                      ay = 0,
                      # Styling annotations' text:
                      font = list(color = '#264E86',
                                  family = 'sans serif',
                                  size = 14))
    fig
}
```

# Analyses {.tabset}

In this pages, countries are aligned so that for each of them day 0 is the day when they each crossed a certain criteria.

## 100th confirmed case

The figure below display the cumulative number of cases over the entire course of the epidemic.
This is different from the number of _active_ cases, which excludes recovered cases and fatalities.

```{r, fig.width=8, fig.height=5, warning=FALSE}
csse_confirmed_table <- csse_confirmed_table %>%
    group_by(`Date`, `Country/Region`) %>%
    summarise(Cases = sum(Cases)) %>% 
    subset(Cases > 100) %>% 
    group_by(`Country/Region`) %>%
    mutate(`Days since 100th case` = row_number() - 1) %>% 
    arrange(`Country/Region`, Date) %>% 
    ungroup()
csse_confirmed_table %>% .plot_function()
```

## 50th confirmed death

```{r, fig.width=8, fig.height=5, warning=FALSE}
csse_deaths_table <- csse_deaths_table %>%
    group_by(`Date`, `Country/Region`) %>%
    summarise(Cases = sum(Cases)) %>% 
    subset(Cases > 50) %>% 
    group_by(`Country/Region`) %>%
    mutate(`Days since 100th case` = row_number() - 1) %>% 
    arrange(`Country/Region`, Date) %>% 
    ungroup()
csse_deaths_table %>% .plot_function()
```
